Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex
"align" command fits better than "split" command here
Update paper.tex
grammar

\begin{equation}
\begin{split}
T_t = c_1 + a_{11}T_{t-1} + a_{12}B_{t-1} + \epsilon_1 \\
B_t = c_2 + a_{21}T_{t-1} + a_{22}B_{t-1} + \epsilon_2
\end{split}
\end{equation}

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. In our research approach we ask the question, if the amount of tweets mentioning Bitcoin in the past, has an effect on the Bitcoin prices in the periods that follow. This question is reflected in the second equation of this model.\\

>>>>

\begin{align}
T_t = c_1 + a_{11}T_{t-1} + a_{12}B_{t-1} + \epsilon_1 \\
B_t = c_2 + a_{21}T_{t-1} + a_{22}B_{t-1} + \epsilon_2
\end{align}

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. The second equation is directly relevant to our research question, as it allows to look into the correlation between present bitcoin price and past tweet count.\\
